---
title: "canWind"
author: "Alex M. Chubaty <achubaty@for-cast.ca>"
date: "01 June 2021"
output: 
  html_document: 
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, fig.path = "figures/",
                      message = FALSE, results = "hold")
```

```{r packages}
if (!require("BioSIM")) {
  ## package BioSIM not available on CRAN nor GitHub; needs to be installed as follows:
  install.packages("https://sourceforge.net/projects/repiceasource/files/latest",
                   repos = NULL,  type = "source")
  install.packages("https://sourceforge.net/projects/biosimclient.mrnfforesttools.p/files/latest",
                   repos = NULL,  type = "source")
}

library("Require")
Require(c(
  "PredictiveEcology/reproducible@development",
  "PredictiveEcology/SpaDES.core@development"#,
  #"PredictiveEcology/LandR@development"
))
```

# Overview

Import/use wind projections from BioSIM.

# Usage

```{r module_usage}
scratchDir <- checkPath("~/scratch/canWind", create = TRUE)

raster::rasterOptions(default = TRUE)
options(
  rasterMaxMemory = 5e+12,
  rasterTmpDir = scratchDir,
  reproducible.cacheSaveFormat = "qs"
)

setPaths(
  cachePath = checkPath(file.path(scratchDir, "cache"), create = TRUE),
  modulePath = file.path(".."),
  inputPath = "data",
  outputPath = "outputs"
)

times <- list(start = 2010, end = 2013)

parameters <- list(
  canWind = list(
    climateModel = "GCM4",
    climateScenario = "RCP45",
    .plotInitialTime = times$start,
    .plotInterval = NA,
    .tempdir = scratchDir,
    years = seq(times$start, times$end, 1)
  )
)
modules <- list("canWind")
objects <- list()
inputs <- list()
outputs <- list()

mySimOut <- simInitAndSpades(times = times, params = parameters, modules = modules, objects = objects)

J4R::shutdownClient()
```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("canWind", "..")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Init

TODO

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("canWind", "..")` may be sufficient.

```{r moduleInputs, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("canWind", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE, eval = TRUE}
df_outputs <- SpaDES.core::moduleOutputs("canWind", "..")
knitr::kable(df_outputs)
```

# Links to other modules

This module prepares data layers for use with MPB red top spread module (<https://github.com/achubaty/mpbRedTopSpread>).
